Skin Lesion Classification on Imbalanced Data Using Deep Learning with Soft Attention

### 2022-10-03 MDPI/sensors-1915564-redo - For Proof - Copy/sensors-1915564.tex
Update Paper Final Version

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{makecell}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{soulutf8}
%\usepackage[adjustmargins]{LatexPackage/trackchanges}
%\addeditor{H.K.D}

@@

\address{$^{1}$ \quad {School} %MDPI: we combined the same affiliation 1 and 3, please confirm.
 of Electrical and Electronic Engineering, Hanoi University of Science and Technology, {Dai Co Viet, Ha Noi 100000, Vietnam;} %MDPI: Please add the city and post code.
{khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct. %H.K.D confirmed
\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, {Ha Noi 115000, Vietnam} %MDPI: Please add the city and post code.
}

@@

		Using the above-mentioned backbones has been attempted previously. Rishu Garg~et~al. \mbox{\cite{03798}} used a transfer learning approach with a CNN-based model: ResNet50 and VGG16 which are pretrained with an ImageNet data set. In addition, they also use data augmentation to avoid an imbalance occurring in  the data set. Histogram equalization is also used to increase the contrast of  skin lesions before being fed into machine learning algorithms including Random Forest, XGBoost, and Support Vector Machine. Histogram equalization can be considered as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performances with an accuracy of 0.90 and  precision of 0.88. However, this approach can be biased since only one skin image of the dataset contains the skin lesion at the center and the background skin, and the histogram may treat the background with increased numbers of occurrence with respect to the same pixel value. In this research study, our proposed method used  Soft-Attention, which can create a heat map feature of the lesion. Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the F1-score and recall at 0.77 and 0.74, respectively.

@@

		Abnormal, skin lesion segmentation, on the other hand, also plays an important role in skin lesion classification. Nawaz~et~al. created a framework for Melanoma segmentation~\mbox{\cite{22750}}. Their proposed method is a Unet model but used  DenseNet77 as the  backbone, and all residual blocks were changed into dense block, which contains a sequence of Convolution and  Average Pooling. This melanoma segmentation approach obtain an accuracy of 0.99. Kadry~et~al. used a Unet model with a VGG deep convolution layer by pooling on the skip connection. This approach can completely extract the entire lesion, although there was an overlap observed with hair. This approach obtained an  accuracy of 0.97.

@@

	\begin{itemize}
	\item[-] Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3;
	\item[-] Using metadata including age, gender, localization as another input of the model;
	\item[-] Using Soft-Attention as a feature extractor of the model;
	\item[-] A new weight loss function.
	\end{itemize}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Materials and Methods}
	\subsection{Materials}
	\subsubsection{Image Data}
	The data set used in this paper is the HAM10000 data set published by the Havard University Dataverse \cite{10417}. There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the Table \ref{table:data-distribution} below:

@@

	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of the mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 \hl{$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm.
 1 with the Soft-Attention module. The NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last normal cell. 
	\begin{figure}[H]
		\includegraphics[width=0.9\linewidth]{Definitions/Mobile Model Structure.PNG}
		\caption{{Mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
 backbone model architecture. This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed mobile model structure}.}
		\label{fig:mobile-model-structure}
	\end{figure}

@@

	The model is evaluated by using the confusion matrix and related metrics. The Figure~\ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for class $2$ . Consider a confusion matrix $A$ with $C$ number of classes. Let $A^i$ and $A^j$ be the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row $i$ and column $k$

@@

	{The last} %MDPI: Please confirm should the no indentation be retained
	% V.D.N confirmed.
 metric is the $AUC$ {(as shown in Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of TP versus the probability of FP.

@@

	\begin{table}[H]
		\caption{Accuracy of all models. ACC stands for accuracy. AD stands for augmented data; this indicates that the model is trained with augmented data. MD stands for metadata, which indicates that the model is trained with metadata. The bold numbers highlight the highest performance.}
		\label{table:overall-acc}
		\setlength{\tabcolsep}{12.38mm}\begin{tabular}{ l  c  c  }
\toprule
\textbf{Model} & \textbf{ACC (AD)} & \textbf{ACC (MD)}\\ 
\midrule
InceptionResNetV2 & 0.79 & \textbf{{0.90} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. 
%H.K.D We have already explain it in the paragraph before the Table 5
}\\
\midrule
DenseNet201 & 0.84 & 0.89\\
\midrule
ResNet50 & 0.76 & 0.70\\
\midrule
ResNet152 & 0.81 & 0.57\\
\midrule
NasNetLarge & 0.56 & 0.84\\
\midrule
MobileNetV2 & 0.83 & 0.81\\
\midrule
MobileNetV3Small & 0.83 & 0.78\\
\midrule
MobileNetV3Large & 0.85 & \textbf{0.86}\\
\midrule
NasNetMobile & 0.84 & \textbf{0.86}\\
\bottomrule
		\end{tabular}
	\end{table}

	Moreover, the model trained with augmented data does not only have low accuracy but their F1-score and the recall also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}. As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an F1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to the Figure \ref{fig:incep f1}. However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the F1-scores on class. The others still face the imbalanced term. Since this data set is not balanced, therefore using augmented data can make the model more biased to the class which has a larger sample. Although using the metadata still leads to model biased, it does contribute to the improvement of the performance of the~model.

	\begin{figure}[H]
		\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=1.3\linewidth]{Definitions/CM/dn201cm}
		\end{minipage}
\caption{{DenseNet201} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
	% H.K.D Citation Provided
 confusion matrix.}\label{fig:densenet201cm}
		\end{figure}\unskip

		\begin{figure}[H]
		\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=1.3\linewidth]{Definitions/CM/irv2cm}
		\end{minipage}
\caption{{InceptionResNetV2} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
% H.K.D Citation Provided
 confusion matrix.}\label{fig:irv2cm}
	\end{figure}

@@

\textls[-15]{	This problem is also true with the recall according to Figures \ref{fig:den recall} and \ref{fig:incep recall}. DenseNet201 and InceptionResNetV2, trained with augmented data have expected recall values of $0.56$ and $0.69$, respectively, while the combination of DenseNet201, Metadata, and the new weight loss function achieve the expected value of recall: $0.82$. Therefore, metadata do improve the model performance by reducing the amount of data needed for achieving higher results. On the other hand, the reason why the model becomes much more balanced is the weighted loss function. Weight loss function has the ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. DenseNet201 and InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$ and $0.82$, respectively, as opposed to their training in akiec without weighted loss function: $0.65$ and $0.37$. }

@@

\bibitem[Author2(year)]{02357-1}
{Shaikh, M.A.;} %MDPI: The label 02357 is repeated. We updated this one, please confirm. % H.K.D it's duplicated with the research paper cited 33, please remove it
 Duan, T.; Chauhan, M.; Srihari, S.N. {In} %MDPI: please add the article title.
 Proceedings of the 2020 17th International Conference on Frontiers in Handwriting Recognition, Dortmund, Germany, 8--10 September 2020.

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{makecell}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{soulutf8}
\usepackage[adjustmargins]{LatexPackage/trackchanges}
\addeditor{H.K.D}

@@

\address{$^{1}$ \quad {School} %MDPI: we combined the same affiliation 1 and 3, please confirm.
 of Electrical and Electronic Engineering, Hanoi University of Science and Technology, {Dai Co Viet, Ha Noi 100000, Vietnam;} %MDPI: Please add the city and post code.
{dung.nguyenviet1@hust.edu.vn, khoi.dh200322@sis.hust.edu.vn} %MDPI: This email address is different from the submitting system. Please confirm which one is correct. %H.K.D confirmed
\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, {Ha Noi 115000, Vietnam} %MDPI: Please add the city and post code.
}

@@

		Using the above-mentioned backbones has been attempted previously. Rishu Garg~et~al. \mbox{\cite{03798}} used a transfer learning approach with a CNN-based model: ResNet50 and VGG16 which are pretrained with an ImageNet data set. In addition, they also use data augmentation to avoid an imbalance occurring in  the data set. Histogram equalization is also used to increase the contrast of  skin lesions before being fed into machine learning algorithms including Random Forest, XGBoost, and Support Vector Machine. Histogram equalization can be considered as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performances with an accuracy of 0.90 and  precision of 0.88. However, this approach can be biased since only one skin image of the dataset contains the skin lesion at the center and the background skin, and the histogram may treat the background with increased numbers of occurrence with respect to the same pixel value. In this research study, our proposed method used  Soft-Attention, which can create a heat map feature of the lesion. Otherwise, Rishu Garg~et~al.'s proposed method also faced the problem of imbalanced classification due to an imbalanced dataset with the F1-score and recall of 0.77 and 0.74, respectively.

@@

		Abnormal, skin lesion segmentation, on the other hand, also plays an important role in skin lesion classification. Nawaz~et~al. created a framework for Melanoma segmentation~\mbox{\cite{22750}}. Their proposed method is a Unet model but used  DenseNet77 as the  backbone, and all residual blocks were changed into dense block, which contains a sequence of Convolution and  Average Pooling. This melanoma segmentation approach obtain an accuracy of 0.99. Kadry~et~al. used a Unet model with a VGG16 deep convolution layer by pooling on the skip connection. This approach can completely extract the entire lesion, although there was an overlap observed with hair. This approach obtained an  accuracy of 0.97.

@@

	\begin{itemize}
	\item[-] Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3;
	\item[-] Using metadata including age, gender, localization as another input of the model;
	\item[-] Using Soft-Attention as a feature extractor of the model;
	\item[-] A new weight loss function.
	\end{itemize}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Materials and Methods}
	\subsection{Materials}
	\subsubsection{Image Data}
	The data set used in this paper is the HAM10000 data set published by the Havard University Dataverse \cite{10417}. There are a total of 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), basal cell carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in Table \ref{table:data-distribution} below:

@@

	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of the mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution layers 1 {$\times$} %MDPI: We revised the "x" into a multiplication sign ("\times" U+00D7). Please confirm.
 1 with the Soft-Attention module. The NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last normal cell. 
	\begin{figure}[H]
		\includegraphics[width=0.9\linewidth]{Definitions/Mobile Model Structure.PNG}
		\caption{{Mobile-based} %MDPI: Please revise the "x" into a multiplication sign ("\times" U+00D7) H.K.D confirm
 backbone model architecture. This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed mobile model structure}.}
		\label{fig:mobile-model-structure}
	\end{figure}

@@

	The model is evaluated by using the confusion matrix and related metrics. Figure~\ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for class $2$ . Consider a confusion matrix $A$ with $C$ number of classes. Let $A^i$ and $A^j$ be the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row $i$ and column $k$

@@

	{The last} %MDPI: Please confirm should the no indentation be retained
	% V.D.N confirmed.
 metric is the $AUC$ {(as shown in Figure \mbox{\ref{fig:AUC}})} score standing for Area Under the Curve which is the Receiver Operating Curve (ROC) that indicates the probability of \textit{TP} versus the probability of \textit{FP}.

@@

	\begin{table}[H]
		\caption{Accuracy of all models. ACC stands for accuracy. AD stands for augmented data; this indicates that the model is trained with augmented data. MD stands for metadata, which indicates that the model is trained with metadata. The bold numbers highlight the highest performance. These results are calculated from the confusion matrix, the two highest model confusion matrices are DenseNet201 and InceptionResNetV2 (as shown in Figure {\mbox{\ref{fig:densenet201cm} and \ref{fig:irv2cm}}})}
		\label{table:overall-acc}
		\setlength{\tabcolsep}{12.38mm}\begin{tabular}{ l  c  c  }
\toprule
\textbf{Model} & \textbf{ACC (AD)} & \textbf{ACC (MD)}\\ 
\midrule
InceptionResNetV2 & 0.79 & \textbf{{0.90} %MDPI: Please add an explanation for bold in the table footer. If the bold is unnecessary, please remove it. 
%H.K.D We have already explain it in the paragraph before the Table 5
}\\
\midrule
DenseNet201 & 0.84 & 0.89\\
\midrule
ResNet50 & 0.76 & 0.70\\
\midrule
ResNet152 & 0.81 & 0.57\\
\midrule
NasNetLarge & 0.56 & 0.84\\
\midrule
MobileNetV2 & 0.83 & 0.81\\
\midrule
MobileNetV3Small & 0.83 & 0.78\\
\midrule
MobileNetV3Large & 0.85 & \textbf{0.86}\\
\midrule
NasNetMobile & 0.84 & \textbf{0.86}\\
\bottomrule
		\end{tabular}
	\end{table}

	Moreover, the model trained with augmented data does not only have low accuracy but their F1-score and recall also are imbalanced according to Figures \ref{fig:den f1}--\ref{fig:incep recall}. As a result, the augmented data model does not classify well in all class as InceptionResNetV2 trained on augmented data has an F1-score on class df and the akiec is just above $0.3$ and $0.4$, separately, while InceptionResNetV2 trained on metadata and the new weight loss can classify well in a balanced way according to Figure \ref{fig:den f1} and \ref{fig:incep f1}. However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depths are equal to or larger than 400 have balanced the F1-scores on class. The others still face the imbalanced term. Since this data set is not balanced, therefore using augmented data can make the model more biased to the class which has a larger sample. Although using the metadata still leads to model biased, it does contribute to the improvement of the performance of the~model.

	\begin{figure}[H]
		\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=1\linewidth]{Definitions/CM/dn201cm}
		\end{minipage}
\caption{{DenseNet201} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
	% H.K.D Citation Provided
 confusion matrix.}\label{fig:densenet201cm}
		\end{figure}\unskip

		\begin{figure}[H]
		\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=1\linewidth]{Definitions/CM/irv2cm}
		\end{minipage}
\caption{{InceptionResNetV2} %MDPI: Please cite the figure in the text and ensure the first citation of each figure appears in numerical order.
% H.K.D Citation Provided
 confusion matrix.}\label{fig:irv2cm}
	\end{figure}

@@

\textls[-15]{	This problem is also true with the recall according to Figures \ref{fig:den recall} and \ref{fig:incep recall}. DenseNet201 and InceptionResNetV2, trained with augmented data have expected recall values of $0.56$ and $0.69$, respectively, while the combination of DenseNet201, Metadata, and the new weight loss function achieve the expected value of recall of $0.82$. Therefore, metadata do improve the model performance by reducing the amount of data needed for achieving higher results. On the other hand, the reason why the model becomes much more balanced is the weighted loss function. Weight loss function has the ability to solve the imbalanced class samples by adding a weight related to the number of samples in each class. DenseNet201 and InceptionResNetV2 trained with the new weighted loss function have recall in akiec of $0.85$ and $0.82$, respectively, as opposed to their training in akiec without weighted loss function: $0.65$ and $0.37$. }

@@
